```{r message=FALSE, warning=FALSE}
library(skimr) #Quick Statistical EDA
library(patchwork) #Create ggplot Patchworks
library(GGally) #Pair Plots
```

# in13

```{r}
in13 <- in13 <- read.csv('Data_files/in13_cleaned.csv')

in13$museo <- as.factor(in13$museo)
in13$prov_museo <- as.factor(in13$prov_museo)
in13$com_museo <- as.factor(in13$com_museo)
in13$datai <- as.Date(in13$datai)
```

```{r}
total_for_models <- read.csv("Data_files/total_for_models.csv", row.names = 1)

total_for_models$churn <- ifelse(total_for_models$si2014 == 0, 1, 0)
total_for_models$si2014 <- NULL
total_for_models$data_nascita <- NULL


total_for_models$riduzione <- as.character(total_for_models$riduzione)

total_for_models$riduzione <- ifelse(total_for_models$riduzione == "OFFERTA CONVENZIONE 28\x80", "OFFERTA CONVENZIONE 28€", total_for_models$riduzione)
total_for_models$riduzione <- ifelse(total_for_models$riduzione == "OFFERTA CONVENZIONE 33\x80", "OFFERTA CONVENZIONE 33€", total_for_models$riduzione)
total_for_models$riduzione <- ifelse(total_for_models$riduzione == "OFFERTA SU QUANTITATIVO 30\x80", "OFFERTA SU QUANTITATIVO 30€", total_for_models$riduzione)
total_for_models$riduzione <- ifelse(total_for_models$riduzione == "OFFERTA SU QUANTITATIVO 44\x80", "OFFERTA SU QUANTITATIVO 44€", total_for_models$riduzione)
total_for_models$riduzione <- ifelse(total_for_models$riduzione == "PASS 60 e VOUCHER OFFERTA 30 \x80 ", "PASS 60 e VOUCHER OFFERTA 30€", total_for_models$riduzione)

total_for_models$riduzione <- as.factor(total_for_models$riduzione)
```




# Descriptive Analysis


## dati1

```{r}
dati1$agegroup <- cut(dati1$eta13, 
                         breaks = c(-Inf, 18, 30, 45, 60, Inf),
                         labels = c("Below 18","18-29",
                                    "30-44","45-59", "60+"),
                         right = FALSE)
```


## in13

```{r}
#levels(in13$museo)
in13_plot= in13 %>% 
  group_by(museo) %>%
  summarise(mean_importo=mean(importo))%>%
  arrange((mean_importo))
```


## an13

```{r}
ggplot(an13)+
  geom_bar(aes(x=tipo_pag, fill=sesso))
  # theme_ipsum_rc(grid="Y")
```


```{r}
an13$comune =as.character(an13$comune)
an13$comune<- iconv(an13$comune, from = "latin1", to = "UTF-8")
an13$comune =as.factor(an13$comune)
#levels(an13$comune)
```



```{r}
an13$agenzia =as.character(an13$agenzia)
an13$agenzia<- iconv(an13$agenzia, from = "latin1", to = "UTF-8")
an13$agenzia =as.factor(an13$agenzia)
#levels(an13$agenzia)
```


```{r}
an13$riduzione <- as.character(an13$riduzione)

an13$riduzione <- ifelse(an13$riduzione == "OFFERTA CONVENZIONE 28\x80", "OFFERTA CONVENZIONE 28€", an13$riduzione)
an13$riduzione <- ifelse(an13$riduzione == "OFFERTA CONVENZIONE 33\x80", "OFFERTA CONVENZIONE 33€", an13$riduzione)
an13$riduzione <- ifelse(an13$riduzione == "OFFERTA SU QUANTITATIVO 30\x80", "OFFERTA SU QUANTITATIVO 30€", an13$riduzione)
an13$riduzione <- ifelse(an13$riduzione == "OFFERTA SU QUANTITATIVO 44\x80", "OFFERTA SU QUANTITATIVO 44€", an13$riduzione)
an13$riduzione <- ifelse(an13$riduzione == "PASS 60 e VOUCHER OFFERTA 30 \x80 ", "PASS 60 e VOUCHER OFFERTA 30€", an13$riduzione)

an13$riduzione <- as.factor(an13$riduzione)
```


```{r fig.dim=c(12,8), dpi=200}
ggplot(an13)+
  geom_bar(mapping=(aes(x=data_nascita, fill=riduzione)))
  # theme_ipsum_rc(grid="Y")
```


```{r fig.dim=c(6,4), dpi=200}
ggplot(data = dati1, aes(x = agegroup)) +
  geom_bar(show.legend = FALSE, fill="#1380A1") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.7) +
  expand_limits(y = 25000)
  # theme_ipsum_rc(grid="Y") +
  # scale_color_ft()
```

The above bar chart shows the overall age of customers. It is observed that the number of customers is the highest with an amount of 32,237 at age ranged 60+ which is the older crowd. 
From age range of 18-29 onwards the frequency of customers increases steadily as the age increase until age ABOVE 60 where a significantly higher frequency of customers was observed. Customers aged below 18 is the lowest at 2,055, this is probably because the company requires the customers to be at least 18 years old to register as a member. Hence, it explains the low number of customers in this range of age.

```{r fig.dim=c(6,4), dpi=200}
ggplot(dati1, aes(x = churn, fill=churn)) +
  geom_bar(show.legend = FALSE) +
  labs(title = "Population of Churners and Non-Churners", 
       x = "Churners", 
       y = "Count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.7) +
  expand_limits(y = 45000) +
  scale_fill_manual(values = c("#1380A1", "#FAAB18"))
  # theme_ipsum_rc(grid="Y")
```

Next, shows the population of churners and non-churners. 0 indicates that they are churners while 1 indicates that they are not churners.

```{r}
dati1$frequency13 <- cut(dati1$nvisit13, 
                         breaks = c(-Inf, 2, 5, 10, 20, Inf),
                         labels = c("0-1", "2-5", "5-9","10-19", "20+"),
                         right = FALSE)
```

```{r fig.dim=c(6,4), dpi=200}
ggplot(dati1, aes(x = frequency13, fill = churn)) +
  geom_bar() +
  scale_fill_manual(values = c("#1380A1", "#FAAB18"))
  # theme_ipsum_rc(grid="Y")
```

When comparing Churner vs SpendFrequencyRange (see Figure 4), it is noticeable that most of the churners (yes) SpendFrequencyRange of 1, 2, 3, and 4-10 which means that they have only spent less than 10 times. Looking at SpendFrequencyRange of 1, it is almost a half-half distribution where there is a close number of churners and 
non-churners. This means that the members under the ‘no’ category could be new members while the members in the ‘yes’ category never continued using the card after once.

```{r fig.dim=c(6,4), dpi=200}
dati1 <- na.omit(dati1)
ggplot(dati1) +
  aes(x = frequency13, fill = sesso) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = c("#FFDAC1", "#FFB7B2"))
  # theme_ipsum_rc(grid="Y")
```

Above shows the spend frequency range of customers against gender. No matter the age range, females always has higher spend frequency range compared to males.

# Variable Selection

## Best Subset Selection


## Data Partition 80/20 Split

```{r}
set.seed(1)
trainIndex <- createDataPartition(dati1$churn, p=.8, list=FALSE)
train_set <- dati1[trainIndex,]
test_set <- dati1[-trainIndex,]
```


## Logistic Regression



