**loading libraries**

```{r}
library(tidyverse)
```

**Importing the CSV files**

```{r}
in13 <- read.csv('Data_files/in13.csv', row.names = 1)
an13 <- read.csv('Data_files/an13.csv', row.names = 1)
dati1 <- read.csv('Data_files/dati1.csv', row.names = 1)
```

# Data cleaning

**Looking for NA values**

```{r}
sum(is.na(in13))
sum(is.na(an13))
sum(is.na(dati1))

# As we can observe, the datasets 'an13' and 'dati1' 
# contains many missing values, while '1n13' has 0 NA.
```

**Now let's analyze each csv singularly:**

##   in13:

### General cleaning

```{r}
in13$prov_museo[in13$museo == "CENTRO FAUNISTICO UOMINI E LUPI"] <- "CN"
in13$com_museo[in13$museo == "CENTRO FAUNISTICO UOMINI E LUPI"] <- "ENTRACQUE"
in13$prov_museo[in13$museo == "MOSTRA BORN SOMEWHERE"] <- "TO"
in13$com_museo[in13$museo == "MOSTRA BORN SOMEWHERE"] <- "TORINO"
```

## an13 & dati1

### Cleaning time variables

```{r}
dati1$ultimo_ing.x <- sub( '(?<=.{6})', '20', dati1$ultimo_ing.x, perl=TRUE)
dati1$abb13 <- sub( '(?<=.{6})', '20', dati1$abb13, perl=TRUE)
dati1$abb14 <- sub( '(?<=.{6})', '20', dati1$abb14, perl=TRUE)
dati1$ultimo_ing.x <- as.Date(dati1$ultimo_ing.x, "%d/%m/%Y")
dati1$abb13 <- as.Date(dati1$abb13, "%d/%m/%Y")
dati1$abb14 <- as.Date(dati1$abb14, "%d/%m/%Y")

an13$data_inizio <- str_sub(an13$data_inizio, end = -7) # remove hours and minutes
an13$data_inizio <- as.Date(an13$data_inizio, "%d/%m/%Y")
```

### Cleaning Cap

```{r}
turin_caps <- c(10121:10156)
turin_caps <- as.character(turin_caps)

#First: create cap for Turin --> 2328
generate_cap_for_turin <- function(comune, cap) {
  if (comune == 'TORINO' && cap == 'XXXXX') {
    cap <- sample(turin_caps, 1, replace = TRUE)
  }
  return(cap)
}


set.seed(1)
an13$cap <- mapply(generate_cap_for_turin, an13$comune, an13$cap)


#second: delete rows with dato mancante and XXXXX --> 181
an13 <- subset(an13, !(comune == 'DATO MANCANTE' & cap == 'XXXXX'))

#third: deleting remaining rows with XXXXX --> 181
an13 <- subset(an13, !( cap == 'XXXXX'))

#see results
# an13 %>% filter(cap=='XXXXX')
```

### Cleaning comune

```{r}
# an13 %>% filter(comune=='DATO MANCANTE') #-->1238
cap <- read_csv('Data_files/Cap.csv', show_col_types = FALSE)
# cap
matching_indices <- match(an13$cap, cap$CAP)

# Identify the rows in 'an13' with missing 'Comune' values ('DATO MANCANTE')
missing_comune_rows <- an13$comune == "DATO MANCANTE"

# Update the missing 'Comune' values in 'an13' using the 'cap' dataset
an13$comune[missing_comune_rows] <- cap$Comune[matching_indices[missing_comune_rows]]
# an13 %>% filter(comune=='DATO MANCANTE')
```

### General cleaning

```{r}
an13 <- an13[an13$data_nascita != "1-01", ]
an13 <- an13[an13$data_nascita != "9-02", ]
an13$data_nascita <- as.integer(an13$data_nascita)
an13 <- an13[an13$data_nascita <2014, ]

# an13 <- an13[an13$comune != "DATO MANCANTE", ]
# an13 <- an13[an13$cap != "XXXXX", ]

an13$agenzia_tipo[an13$agenzia == "ASSOCIAZIONE TORINO CITTA' CAPITALE EURO"] <- "ASSOCIAZIONE"
an13$agenzia_tipo[an13$agenzia == "LICEO SCIENTIFICO GALILEO FERRARIS"] <- "OFFERTA SCUOLE "
colnames(an13)[colnames(an13) == "OFFERTA SCUOLE "] <- "OFFERTA SCUOLE"

an13 <- an13[an13$cap != "10.12", ]
an13 <- an13[an13$cap != "BIANC", ]
an13 <- an13[an13$cap != "\xa0 100", ]
an13 <- an13[an13$cap != "100", ]
an13 <- an13[an13$cap != "10000", ]
an13 <- an13[an13$cap != "10007", ]
an13 <- an13[an13$cap != "CORSO", ]
an13 <- an13[an13$cap != "ESTER", ]
an13 <- an13[an13$cap != "L2210", ]
an13 <- an13[ nchar(an13$cap) >= 5, ]

an13$cap[an13$codcliente == 14061] <- "10129"
an13$cap[an13$codcliente == 127888] <- "10124"
an13$cap[an13$codcliente == 199123] <- "10145"
an13$cap[an13$codcliente == 203569] <- "10048"
an13$cap[an13$codcliente == 211576] <- "10125"
```


### Merging

```{r}
total <- merge(an13, dati1, by="codcliente", all.x = TRUE)
```

```{r}
sapply(total, function(x) sum(is.na(x)))
```

```{r}
total <- total[, !(names(total) %in% c('sesso.y', 'prezzo13', 'prov', 'professione'))]
colnames(total)[colnames(total) == "sesso.x"] <- "sesso"

total["nvisite0512"][is.na(total["nvisite0512"])] <- 0
total["nmusei0512"][is.na(total["nmusei0512"])] <- 0
```

### Changing variable type

```{r}
total$sesso <- as.factor(total$sesso)
total$sconto <- as.factor(total$sconto)
total$riduzione <- as.factor(total$riduzione)
total$tipo_pag <- as.factor(total$tipo_pag)
total$agenzia <- as.factor(total$agenzia)
total$agenzia_tipo <- as.factor(total$agenzia_tipo)
total$comune <- as.factor(total$comune)
total$cap <- as.integer(total$cap)
total$nuovo_abb <- as.factor(total$nuovo_abb)

total$si2013 <- as.factor(total$si2013)
total$si2014 <- as.factor(total$si2014)
total$cambiocap0512 <- as.factor(total$cambiocap0512)
```


```{r}
sapply(total, function(x) sum(is.na(x)))
```

### Creating dataset for models

```{r}
total_for_models <- total[, c(-2, -14, -23, -24, -25)]
```

```{r}
total_for_models <- total_for_models[!is.na(total_for_models$cambiocap0512), ]
```

```{r}
sapply(total_for_models, function(x) sum(is.na(x)))
```
```{r}
total_for_models <- na.omit(total_for_models)
```

```{r}
total <- total[!is.na(total$abb13), ]
total <- total[!is.na(total$sesso), ]
total <- total[!is.na(total$comune), ]
```

```{r}
sapply(total, function(x) sum(is.na(x)))
```
#merging the in13 and total dataset by client code
```{r}

in13_total <- merge(in13, total, by.x ="CodCliente", by.y = "codcliente", all.x = TRUE)

sapply(in13_total, function(x) sum(is.na(x)))

```
```{r}
in13_total <- in13_total[!is.na(in13_total$sesso), ]
sapply(in13_total, function(x) sum(is.na(x)))
```
#changing variables types and adding new variables
```{r}
in13_total$datai <- as.Date(in13_total$datai, "%d/%m/%Y") 
in13_total$churn <- ifelse(in13_total$si2014 == 0, 1, 0)
in13_total$churn <- as.factor(in13_total$churn)
in13_total$CodCliente <- as.factor(in13_total$CodCliente)
in13_total$museo <- as.factor(in13_total$museo)
in13_total$prov_museo <- as.factor(in13_total$prov_museo)
in13_total$com_museo <- as.factor(in13_total$com_museo)
```

```{r}
library(plyr)
in13_total$riduzione <- revalue(in13_total$riduzione, c("OFFERTA SU QUANTITATIVO 44\x80" = "OFFERTA SU QUANTITATIVO 44€", "OFFERTA CONVENZIONE 28\x80" = "OFFERTA CONVENZIONE 28€", "PASS 60 e VOUCHER OFFERTA 30 \x80 " = "PASS 60 e VOUCHER OFFERTA 30€", "OFFERTA SU QUANTITATIVO 30\x80" = "OFFERTA SU QUANTITATIVO 30€", "OFFERTA CONVENZIONE 33\x80" = "OFFERTA CONVENZIONE 33€"))

levels(in13_total$riduzione)
```


```{r}
library(dplyr)
in13_total %>% 
  group_by(sesso) %>%
  summarize ("Number of observations"= n(),
             "Subscription" = round(mean(nabb0512),2),
             "Number of Visits in 2013"=round(mean(nvisit13),0),
             "Number of Musuem Visited in 2013"=round(mean(nmus13),2),
             "Average Annual Price"=round(mean(importo.y),2))
```


```{r}
library(gridExtra)
library(GGally)

g1 <- in13_total %>% 
  ggplot(aes(x=churn, y=nabb0512, fill=fct_rev(churn))) + 
  geom_bar(stat="summary", fun="mean", show.legend=F) + 
  stat_summary(aes(label=paste(round(after_stat(y), 0), "years")), fun=mean, geom="text", size=3.5, vjust = -0.5) + 
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn")) +
  labs(title = "Average Subscription", x = "Churn", y = "Subscription Duration" )

g2 <- in13_total %>% 
  ggplot(aes(x=churn, y=importo.y, fill=fct_rev(churn))) +
  geom_bar(stat="summary", fun="mean", show.legend=F) + 
  stat_summary(aes(label = paste(round(after_stat(y), 0), "euros")), fun=mean, geom="text", size=3.5, vjust = -0.5) + 
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn")) +
  labs(title = "Average Annual Price", x = "Churn", y = "Average Price")

grid.arrange(g1, g2, ncol = 2, nrow = 1)
```


#From the histograms above, we can see that customers who churn are having fewer yearly subscription and higher average annual price.

```{r fig.dim=c(6,4), dpi=200}
g3 <- in13_total %>% 
  ggplot(aes(x=tipo_pag, fill=fct_rev(churn)))+  
  geom_bar(position = "dodge", show.legend = TRUE) + 
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.7, size = 3, position = position_dodge(.7)) +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn")) +
  labs(title="Customer Churn by Payment Method", y="Count of Payment Method", x = "Type of Payment", fill = "Churn Status")
g3

```
#creating a variable called "Agegroup", to classify the age into different age groups
```{r}
# Calculate the percentages and create a new data frame
percentage_data <- in13_total %>%
  group_by(tipo_pag, churn) %>%
  summarize(count = n()) %>%
  group_by(tipo_pag) %>%
  mutate(percentage = round(count / sum(count)*100),2)

# Create the plot
ggplot(data = percentage_data, aes(x = tipo_pag, y= percentage, fill = fct_rev(churn))) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(percentage, "%"), group = churn), 
            position = position_dodge(-.7), vjust = -0.3, size = 3) +
  labs(title = "Customer Churn By Payment Method", y = "Percentage", x = "Type of Payment", fill = "Churn Status") +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn"))


```




```{r fig.dim=c(6,4), dpi=200}
# Create age group variable
in13_total$agegroup <- cut(in13_total$eta13, 
                         breaks = c(-Inf, 18, 30, 45, 60, Inf),
                         labels = c("Below 18","18-29",
                                    "30-44","45-59", "60+"),
                         right = FALSE)

# Create the plot
ggplot(data = in13_total, aes(x = agegroup, fill = fct_rev(churn))) +
  geom_bar(position = "dodge", show.legend = TRUE) + 
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.7, size = 3, position = position_dodge(.9)) +
  labs(title = "Customer Churn By Age Group", y = "Count of Agegroup", fill = "Churn Status") +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn"))


```
```{r}

```



```{r fig.dim=c(6,4), dpi=200}
g5 <- in13_total %>% 
  ggplot(aes(x=sesso, fill=fct_rev(churn)))+  
  geom_bar(position = "dodge", show.legend = TRUE) + 
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.6, size = 3,  position = position_dodge(.9)) +
  labs(title="Customer Churn by Gender", y="Count", x = "Gender", fill = "Churn Status") +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn"))

g5
```
```{r}
library(lubridate)
museum_data <- in13_total %>%
  mutate(visit_month = floor_date(datai, unit = "month")) %>%
  group_by(visit_month, churn, museo) %>%
  summarize(visit_count = n(), .groups = "drop")

ggplot(museum_data, aes(x = visit_month, y = visit_count, fill = factor(churn))) +
  geom_col(position = "dodge", show.legend = TRUE) +
  labs(
    title = "Monthly Museum Visits Over Time by Churn Status",
    x = "November 2012 - December 2013",
    y = "Number of Visits",
    fill = "Churn Status"
  ) +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn")) +
  theme_minimal() +
  scale_x_date(date_labels = "%b", date_breaks = "1 month")

```

```{r}
reduction_summary <- in13_total %>%
  group_by(riduzione, churn) %>%
  summarise(client_count = n())
  

ggplot(reduction_summary, aes(x = client_count, y = riduzione, fill = factor(churn))) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    title = "Churn by Reduction Type",
    x = "Number of Customers",
    y = "Reduction Type",
    fill = "Churn Status"
  ) +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn")) +
  theme_minimal()
```

```{r fig.dim=c(6,4), dpi=200}
ggplot(in13_total, aes(x = sesso, fill=sesso)) +
  geom_bar(show.legend = TRUE) +
  labs(title = "Distribution of Customer by Gender", 
       x = "Gender", 
       y = "Count",
       fill = "Gender") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.7, size = 3, position = position_dodge(.9)) +
  scale_fill_manual(values = c("F" = "#4e79a7", "M" = "#f28e2b"), labels = c("F" = "Female", "M" = "Male")) 

# Convert to a pie chart
  #coord_polar(theta = "y") +
  
# Remove the x and y-axis labels
  #theme_void()
```
```{r fig.dim=c(6,4), dpi=200}
ggplot(in13_total, aes(x = 1, fill=sesso)) +
  geom_bar(width = 1) +
  labs(title = "Distribution of Customer by Gender", 
       x = "Gender", 
       y = "Count",
       fill = "Gender") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.7, size = 5, position = position_stack(.5)) +
  scale_fill_manual(values = c("M" = "#4e79a7", "F" = "#f28e2b"), labels = c("F" = "Female", "M" = "Male")) +

# Convert to a pie chart
  coord_polar(theta = "y") +
  
# Remove the x and y-axis labels
  theme_void()
```
```{r}
# Calculate the count of each gender
gender_counts <- in13_total %>% count(sesso)

# Create a pie chart
ggplot(gender_counts, aes(x = "", y = n, fill = sesso)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
    geom_text(aes(label = paste0(n,
                               " (",
                               scales::percent(n / sum(n)),
                               ")")),
            position = position_stack(vjust = 0.5)) +
  labs(
    title = "Distribution of Customers by Gender",
    x = NULL,
    y = NULL,
    fill = "Gender"
  ) +
  scale_fill_manual(values = c("M" = "#4e79a7", "F" = "#f28e2b"), labels = c("F" = "Female", "M" = "Male")) +
  theme_void()

```



```{r fig.dim=c(6,4), dpi=200}
churn_counts <- in13_total %>% count(churn)

ggplot(churn_counts, aes(x = "", y = n, fill = churn)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  geom_text(aes(label = paste0(n,
                               " (",
                               scales::percent(n / sum(n)),
                               ")")),
            position = position_stack(vjust = 0.5)) +
  labs(title = "Distribution of Customer by Churn", 
       x = NULL, 
       y = NULL,
       fill = "Churn Status") +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn")) +

# Remove the x and y-axis labels
  theme_void()
```



```{r fig.dim=c(6,4), dpi=200}
ggplot(in13_total, aes(x = churn, fill=churn)) +
  geom_bar(show.legend = TRUE) +
  labs(title = "Distribution of Churn", 
       x = "Churn", 
       y = "Count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.3, size = 3, position = position_dodge(.9)) +
  scale_fill_manual(values = c("0" = "#4e79a7", "1" = "#f28e2b"), labels = c("0" = "No Churn", "1" = "Churn"))
  
```
```{r fig.dim=c(6,4), dpi=200}
ggplot(data = in13_total, aes(x = agegroup)) +
  geom_bar(show.legend = TRUE, fill="#1380A1") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust =-0.5, size = 3, position = position_dodge(.9)) +
  labs(title = "Distribution By Age Group", y = "Count")
  
```

```

