```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


# Cost

#CLV

# First part: COSTS
```{r}
in13 <- read.csv("Data_files/in13.csv", row.names = 1)


in13_forCLV= in13%>%
  group_by(CodCliente) %>%
  summarize(sum=sum(importo))%>%
  arrange(desc(sum))

in13_forCLV
mean_value= sum(in13_forCLV$sum)/nrow(in13_forCLV)
mean_value
```

30.66 euros is the mean amount of euro that each customer would spend if he/she wouldn't have a card.
Because the card-association pays each museum 50% of the real price for each visit, they pay around 15 euros annually for each customer.

# Second part: REVENUES

```{r}
an13 <- read.csv("Data_files/an13.csv", row.names = 1)

an13_forCLV= an13%>%
  select(codcliente,importo)%>%
  summarize(sum=sum(importo)/nrow(an13))

an13_forCLV
```

So the card society gains from each customer: 35-15= 20 euros (on average). 
Anyway, we must consider that 20 euros is the Customer Value, but we need the Customer Lifetime Value:


```{r}
dati1 <- read.csv("Data_files/dati1.csv", row.names = 1)

dati1_forCLV= dati1%>%
  select(codcliente,eta13)%>%
  summarize(mean_age=mean(eta13))

dati1_forCLV
```

The mean age is 52 years. Considering a normal lifetime of about 86 years, we obtain the CLV:
CLV=(86-52)x20 = 34x20 = 760 euros

